---
title: "Change in Freedom from 2013 to 2023"
subtitle: "A comparison of censorship among great powers"
author: "Zichu Yang"
institute: "American University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    self_contained: yes
    lib_dir: libs
    css: [default, tamu, tamu-fonts]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---
class: center, middle

#Data and Methodology


---

# Freedom House

Dataset: 

- Freedom in the World 2023 edition

--

Methodology and Logic:

- Based on Universal Declaration of Human Rights

--

- Using detailed questionaire for each category to calculate score

--

- Focusing on implementation of freedom on individual level 

---
class: center, middle

#Analysis 1


---
class: middle

# Freedom of Expression and Belief

```{r setup, eval=TRUE, include=FALSE}
library(tidyverse)
library(readxl)
library(patchwork)
library(ggbreak)

free = read_excel('freedomhouse.xlsx')

free2 = 
  filter(free, `Country/Territory`=='China'|
           `Country/Territory`=='Russia'|
           `Country/Territory`=='France'|
           `Country/Territory`=='United States'|
           `Country/Territory`=='United Kingdom')
```

```{r, fig.asp = 3/4, fig.align = 'center', eval=TRUE, include=TRUE,echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', dpi=200}

ggplot(free2,aes(Edition,D))+
  geom_line(aes(color=`Country/Territory`),alpha=1,size=1.5)+
  scale_x_continuous(breaks = seq(2012, 2023, by = 1))+
  labs(x='Year',y="Freedom of Expression and Belief")+
  theme(panel.background = element_rect(fill = "#bababa"))+
  scale_color_brewer(palette="RdYlBu")

```

Mean: 10.5  Median: 12  Max: 16  Min: 0

---
class: center, middle

#Analysis 2


---

# How Civil Liberties affected individual Freedom

```{r, fig.asp = 3/4, fig.align = 'center', eval=TRUE, include=TRUE,echo=FALSE, message=FALSE, warning=FALSE, out.width='70%', dpi=200}
p1 = 
  ggplot(free2,aes(Edition,Total))+
  geom_line(aes(color=`Country/Territory`),alpha=1,size=1)+
  scale_x_continuous(breaks = seq(2012, 2023, by = 1))+
  labs(x='Year',y="Total Score")+
  scale_y_break(c(30,80))+
   theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank(),
        axis.line.x.top = element_blank(),
        panel.background = element_rect(fill = "#bababa"))+
  scale_color_brewer(palette="RdYlBu")

p2 =
  ggplot(free2,aes(Edition,CL))+
  geom_line(aes(color=`Country/Territory`),alpha=1,size=1)+
  scale_x_continuous(breaks = seq(2012, 2023, by = 1))+
  labs(x='Year',y="Civil Liberties Score")+
  scale_y_break(c(20,50))+
   theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank(),
        axis.line.x.top = element_blank(),
        panel.background = element_rect(fill = "#bababa"))+
  scale_color_brewer(palette="RdYlBu")

p1/p2
```
Total Score: Mean=57.6 Median=61

CL Score: Mean=34.8 Median=35
